JAGS Model

### 2020-03-04 Rcodes/JAGS_overdoses.Rmd
pdf generated

Pre-set variables.
```{r Defining Values}
n_T <-  length(df$o_t) # we have 12 samples
n_a <- 1000
N <- 10000
u_t <- df$u_t
x_a <- df$x_a
```

@@

```{r include=FALSE}
plot(samples)
```
# q1: what is the equivalent plot that we can see we have enough iteration?

@@

pst_mtx = as.matrix(samples)
temp = pst_mtx[,1:12]
p_a <- pst_mtx[,13]
head(temp)
length(p_a)
colnames(temp) <- seq(1,12)
df_o_t <- as.data.frame(temp)
head(df_o_t)
str(df_o_t)
```

@@

```{r}
df_u_t <- data.frame()

for (i in 1:m) {
  obs <- rbinom(n=12,size = as.numeric(df_o_t[i,]),prob =p_a[i])
  df_u_t=rbind(df_u_t,obs)
}
colnames(df_u_t) <- factor(seq(1,12),levels = seq(1,12))
str(df_u_t)
```

@@

  ## tidy x_a
  df_x_a <- vector() 
  for (i in 1:n) {
    obs <- rbinom(m,n_a,p_a)
    df_x_a <- cbind(df_x_a,obs)
  }
  colnames(df_x_a) <- seq(1:12)
  df_x_a <- as.data.frame(df_x_a)
  ppc_x_a <- gather(df_x_a, key = 'month',value = 'x_a')
  ppc_x_a$month <- factor(ppc_x_a$month,levels = seq(1,12))
  ppc = list('u_t'=ppc_u_t, 'x_a'=ppc_x_a)
  mylist=list('data'=df,'model'=simple.model,'trace'=trace_o_t,'ppc'=ppc)
  return (mylist)
}

>>>>

Pre-set variables.  
```{r Defining Values}
n_T <- length(df$o_t)
n_a <- 1000
N <- 10000
u_t <- df$u_t
x_a <- df$x_a
```

@@

```{r include=FALSE}
# plot(samples)
```
# q1: what is the equivalent plot that we can see we have enough iteration?

@@

pst_mtx = as.matrix(samples)
temp = pst_mtx[,1:12]
p_a <- pst_mtx[,13]
head(temp)
length(p_a)
colnames(temp) <- seq(1,12)
df_o_t <- as.data.frame(temp)
head(df_o_t)

@@

```{r}
df_u_t <- data.frame()
m=length(p_a)
for (i in 1:m) {
  obs <- rbinom(n=12,size = as.numeric(df_o_t[i,]),prob =p_a[i])
  df_u_t=rbind(df_u_t,obs)
}
colnames(df_u_t) <- factor(seq(1,12),levels = seq(1,12))
str(df_u_t)
```

@@

  ## tidy x_a
  df_x_a <- vector() 
  for (i in 1:n_T) {
    obs <- rbinom(m,n_a,p_a)
    df_x_a <- cbind(df_x_a,obs)
  }
  colnames(df_x_a) <- seq(1:12)
  df_x_a <- as.data.frame(df_x_a)
  ppc_x_a <- gather(df_x_a, key = 'month',value = 'x_a')
  ppc_x_a$month <- factor(ppc_x_a$month,levels = seq(1,12))
  ppc = list('u_t'=ppc_u_t, 'x_a'=ppc_x_a)
  mylist=list('data'=df,'model'=simple.model,'trace'=trace_o_t,'ppc'=ppc)
  return (mylist)
}
